---
title: "Victims of auschwitz"
author: 
  - Ahnaf Alam
thanks: "Code and data are available at https://github.com/AhnafAlam1/holocaust_data and app can be found at https://652r5n-ahnaf-alam.shinyapps.io/apps/ "
date: today
date-format: long
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
library(readxl)
library(ggplot2)


df <- read_csv(here::here("df.csv"))


```




```{r}
#| warning: false
#| message: false
#| echo: false

df <- df |>
  rename(
    ethnicity = Birthplace,
    last_name = `Last Name`
  )

```


# Discussion

## What We Did

In the  article titled "We Still Can’t See American Slavery for What It Was" by @Bouie_2022, the author delves into topics that is pertinent to what we pursued in this project. Our venture involved the meticulous utilization of Holocaust data, specifically from Auschwitz, to meticulously evaluate all those who tragically perished during World War II. Using the `shiny` library [@shiny], we meticulously crafted an interactive app, delving into the nuanced analysis of those who met their fates at Auschwitz, categorized by their respective ethnic backgrounds. The dataset procured for our app was meticulously curated from the archives maintained by @data.

## Data Insights

The dataset comprises of preserved Death Books or Sterbebücher originating from the Auschwitz concentration camp in Poland, between the period from July 29, 1941, to December 31, 1943. It provides a comprehensive array of information, including the first names and last names of the unfortunate victims, along with records of their dates of birth, dates of death, birthplaces, residences, and religious affiliations. Given the lack of explicit ethnicity data within the dataset, we infer ethnic backgrounds based on birthplace, making it a pivotal component for our analytically framework.

## Insights in the Data

The author  observes that out of the 12.5 million individuals captured during the slave trade era, only 10.7 million individuals ultimately reached the so-called "new world." This striking comparison underscores the scale of the atrocities witnessed, juxtaposed against the relatively modest dataset of 65,280 individuals meticulously documented at Auschwitz during the stipulated time frame.

Furthermore, the author draws attention to the invaluable resource that is the SlaveVoyages database, meticulously cataloging intricate details of individual ships, voyages, and even the individuals ensnared in the brutal machinery of the slave trade. This repository, akin to the United States Holocaust Memorial Museum database, serves as an invaluable trove for scholarly exploration, unlocking unprecedented avenues for nuanced research and shedding light on previously obscured historical narratives.

## Identification Framework

In pondering the ethical conundrum posed by the ability to identify specific enslaved individuals, we reflect upon a parallel inquiry in our project. Our app's functionality allows users to delve into the intricate tapestry of ethnicity or birthplace, facilitating the identification of individuals based on their first and last names alongside their ethnic affiliations. This feature carries profound significance, offering solace to individuals seeking to trace their familial roots amidst the harrowing annals of the Holocaust.

## Data Limitations

The poignant observation that no dataset, regardless of its precision, can be deemed exhaustive rings true across historical datasets. While the empirical rigor of spreadsheet-based analysis aids scholarly endeavors, it is imperative to approach such data with sensitivity and empathy. Each data point represents not merely an abstract statistic but a poignant testament to the lived experiences of real human beings, imbued with emotions, aspirations, and familial bonds. Failure to acknowledge this reality risks perpetuating ethical transgressions within our analytical frameworks.

## Data Origins

Bouie incisively highlights the disquieting reality that the availability of data on the slave trade owes its existence not to altruistic motives but rather to the pragmatic imperatives of commercial and legal documentation. This stark observation is equally applicable to the dataset culled from Auschwitz, painstakingly compiled by German forces and preserved within the confines of meticulously maintained ledgers, ominously titled Sterbebücher, or death books. It behooves us to confront the inherent moral quandaries surrounding the utilization of such data, mindful of the profound human toll exacted by the historical events they encapsulate.





\newpage


# References


